Matching Bullets

### 2015-12-09 imaging-paper.Rnw
couple of edits

Rifling in the barrel creates striation marks on the bullet during the firing process (and grooves). These marks are claimed to be unique to the barrel, as described in a 1992 AFTE article \cite{afte:1992}. ``The theory of identification as it pertains to the comparison of toolmarks enables opinions of common origin to be made when the \emph{unique surface contours} of two toolmarks are in sufficient agreement" The article goes on to state that ``Significance is determined by the comparative examination of two or more sets of surface contour patterns comprised of individual peaks, ridges and furrows." \footnote{\url{https://www.ncjrs.gov/app/publications/Abstract.aspx?id=254151}}, \footnote{AFTE 1992 theory of identification \url{http://projects.nfstc.org/firearms/module09/fir_m09_t05_05.htm}}

@@

\section{Approach to automatic matching}
Applying the  loess fit to a range of different surface cross cuts (see Figures~\ref{fig:manualmatch} and Figure~\ref{fig:manualmatch}, with cross cuts from 50 to 150) shows the striation marks across two bullets. Cross cuts of bullet 1 are shown on the left (cross cuts with values below 100) and cross cuts of bullets 2 are shown on the right (cross cuts with values above 100). A lot of the striation marks align, allowing for an easy visual assessment of the shared similarities between the two bullets.

@@

@@

grid.arrange(list_of_matches[[1]], list_of_matches[[2]], list_of_matches[[3]], 
             list_of_matches[[4]], list_of_matches[[5]], list_of_matches[[6]],
             ncol = 1)
@
\caption{\label{fig:barrel2}All lands from the first bullet shot from barrel 2 are compared to the first land of the second bullet shot from barrel 2. The largest number of CMS is eleven, observed with land six of the first bullet. }
\end{figure}
\afterpage{clearpage}

>>>>

Rifling in the barrel creates striation marks on the bullet during the firing process (and grooves). These marks are claimed to be unique to the barrel, as described in a 1992 AFTE article \cite{afte:1992}. ``The theory of identification as it pertains to the comparison of toolmarks enables opinions of common origin to be made when the \emph{unique surface contours} of two toolmarks are in sufficient agreement" The article goes on to state that ``Significance is determined by the comparative examination of two or more sets of surface contour patterns comprised of individual peaks, ridges and furrows." %\footnote{\url{https://www.ncjrs.gov/app/publications/Abstract.aspx?id=254151}}

@@

\section{Approach to automatic matching}
Applying the  loess fit to a range of different surface cross cuts (see Figures~\ref{fig:manualmatch} and~\ref{fig:manualmatch-rgl}, with cross cuts from 50 to 150) shows the striation marks across two bullets. Cross cuts of bullet 1 are shown on the left (cross cuts with values below 100) and cross cuts of bullets 2 are shown on the right (cross cuts with values above 100). A lot of the striation marks align, allowing for an easy visual assessment of the shared similarities between the two bullets.

@@

\subsection{Varying smoothing factor}
\hh{XXX it would be good to have a discussion of the smoothing factor XXX}

@@

grid.arrange(list_of_matches[[1]], list_of_matches[[2]], list_of_matches[[3]], 
             list_of_matches[[4]], list_of_matches[[5]], list_of_matches[[6]],
             ncol = 1)
@
\caption{\label{fig:barrel2}All lands from the first bullet shot from barrel 2 are compared to the first land of the second bullet shot from barrel 2. The largest number of CMS is eleven, observed with land six of the first bullet. }
\end{figure}
